Working title: Ecological network control

### 2018-05-18 paper/manuscript.Rmd
Add superior/subordinate to description of figure of structural control

The first step before applying methods of control theory is to construct a directed network that is able to provide an indication of the extent to which species affect each others abundance. 
In some ecological networks, establishing the directionality can be relatively straightforward, for example when links represent biomass transfer or energy flow [@isbell_human_2013]. 
In pollination networks, however, this directionallity is less obvious as both species can in theory benefit from the interaction. 
We overcome that obstacle by noting that the extent to which species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@bascompte_asymmetric_2006]. 
This asymmetry is given by $$a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )},$$ where the dependence of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits from pollinator *j* compared to all pollinator visits to plant *i*. 
Previous research has shown that mutualistic interactions are often highly asymmetric in natural communities; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa). 
We then create a directed link between species *i* and *j* when $d_{ij}-d_{ji} \geq 0$ to establish the most likely direction of control between a species pair (Figure \@ref(fig:fig-example-networks)a). 
By basing the direction of the links on the asymmetry of their dependence, we are able to generate a network that is consistent with the dynamics of the community while satisfyingh the requirements of structural controllability. 
```{r}
drake::loadd(fig_struct_control)
```

```{r fig-example-networks, fig.width=fig_struct_control$width, fig.height=fig_struct_control$height, fig.cap="(a) To establish the direction of control we start with a weighted visitation network (on the right). In this network, the width of the links correspond to the frequency of visitation. We then calculate the dependencies between species pairs and create a directed network (left) in which the direction of the links correspond to the direction of the assymetry of their dependence. For instance, the population of plant $p_1$ is likely to be affected by the population of pollinator $a_1$ to a larger extent that the population of $a_1$ depends on $p_1$ because $a_1$ interacts more strongly with other species in the community; hence the direction of control between these two species can be simplyfied with a directed link from $a_1$ to $p_1$. (b) A system is structurally controllable if there are no inaccessible links or dilations. The network on the bottom left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously. The network in the bottom right  is not controllable because node $x_3$ is inaccessible from the input node $u_1$ in the system. Both systems can be made controllable by adding an extra input node (top)."}
replayPlot(fig_struct_control$plot)
```

>>>>

The first step before applying methods of control theory is to construct a directed network that is able to provide an indication of the extent to which species affect each others abundance. 
In some ecological networks, establishing the directionality can be relatively straightforward, for example when links represent biomass transfer or energy flow [@isbell_human_2013]. 
In pollination networks, however, this directionallity is less obvious as both species can in theory benefit from the interaction. 
We overcome that obstacle by noting that the extent to which species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@bascompte_asymmetric_2006]. 
This asymmetry is given by $$a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )},$$ where the dependence of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits from pollinator *j* compared to all pollinator visits to plant *i*. 
Previous research has shown that mutualistic interactions are often highly asymmetric in natural communities; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa). 
We therefore create a directed link between species *i* and *j* when $d_{ij}-d_{ji} \geq 0$ to establish the most likely direction of control between a species pair (Figure \@ref(fig:fig-example-networks)a). 
By basing the direction of the links on the asymmetry of their dependence, we are able to generate a network that is consistent with the dynamics of the community while satisfyingh the requirements of structural controllability. 
```{r}
drake::loadd(fig_struct_control)
```

```{r fig-example-networks, fig.width=fig_struct_control$width, fig.height=fig_struct_control$height, fig.cap="(a) To establish the direction of control we start with a weighted visitation network (on the right). In this network, the width of the links correspond to the frequency of visitation. We then calculate the dependencies between species pairs and create a directed network (left) in which the direction of the links correspond to the direction of the assymetry of their dependence. For instance, the population of plant $p_1$ is likely to be affected by the population of pollinator $a_1$ to a larger extent that the population of $a_1$ depends on $p_1$ because $a_1$ interacts more strongly with other species in the community; hence the direction of control between these two species can be simplyfied with a directed link from $a_1$ to $p_1$. (b) A system is structurally controllable if there are no inaccessible links or dilations. The network on the bottom left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously, in other workds there are less superiors ($x_2$) than subordinates ($x_1$ and $x_2$ ). The network in the bottom right  is not controllable because node $x_3$ is inaccessible from the input node $u_1$ in the system. Both systems can be made controllable by adding an extra input node (top)."}
replayPlot(fig_struct_control$plot)
```
